---
title: "Programs"
---
<center>
<a href="#youth-formation-division">YOUTH FORMATION DIVISION</a><br>
<a href="#school-management-monitoring-evaluation-smme">SCHOOL MANAGEMENT MONITORING & EVALUATION (SMM&E)</a><br>
<a href="#national-greening-program-ngp">National Greening Program</a><br>
<a href="#school-inside-a-garden-siga">School Inside a Garden</a><br>
<a href="#student-government-ssgspg">Student Government</a><br>
<a href="#we-advocate-time-consciousness-and-honesty-watch">W.A.T.C.H.</a><br>
<a href="#youth-for-environment-in-schools-organization-yes-o">YES-O</a><br>
</center>

## **YOUTH FORMATION DIVISION**

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/bkd",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## **SCHOOL MANAGEMENT MONITORING & EVALUATION (SMM&E)**

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/cpp",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## Gulayan sa Paaralan Program (GPP)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/gpp",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## National Greening Program (NGP)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/ngp",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## School Inside a Garden (SIGA)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/siga",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## Student Government (SSG/SPG)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/ssg",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## We Advocate Time Consciousness and Honesty (WATCH)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/watch",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>


## Youth for Environment in School’s Organization (YES-O)

```{r, echo=FALSE}
library(slickR)
slickR(list.files("D:/Website/YFD/Del_Sur_YFD/carousel/yeso",  full.names = TRUE), height = 200, width = '95%')+settings(dots=TRUE, initialSlide = 0, slidesToShow = 3, slidesToScroll = 3, focusOnSelect = TRUE, autoplay = TRUE)
```

text~text~text~text

<p align="right">
<a href="#top">Back to top</a>
</p>
